\Title

### 2021-06-25 manuscript/content.tex
Review the end of the introduction

In the present study,
we propose a two strategies for reducing the computational load of
the equivalent sources technique:

@@

The first strategy consists in dividing the survey area into horizontal blocks
and assign one source to each block, located at the median horizontal location
of the data points. For airborne, shipborne, and satellite surveys, which are
oversampled along tracks, this can greatly reduce the size of the inverse
problem while retaining the same quality of interpolation.

The gradient boosting algorithm allows us to fit the equivalent source model
iteratively by operating on individual overlapping windows.
Thus, our method solves several much smaller least-squares problems instead of
a large one.
This has some similarities with the strategy used by \citet{leao1989} but
without the requirement for sources and predictions to be on regular grids.

Through tests on synthetic data, we show that:
(i)~the \emph{block-averaged} sources are able to achieve the same accuracy as
other traditional equivalent source layouts while using a fraction of the
number of sources, and
(ii)~the \emph{gradient boosting} algorithm greatly reduces the computational
memory required to fit very large datasets without sacrificing prediction
accuracy.
Finally, a combination of both strategies is used to process a collection of
around 1.7 million ground gravity data measurements from Australia.

>>>>

In the present study,
we propose two strategies for reducing the computational load of
the equivalent sources technique:

@@

The first strategy consists in dividing the survey area into horizontal blocks
and assigning a single source to each block, located at the median horizontal
location of the data points.
For airborne, shipborne, and satellite surveys, which are oversampled along
tracks, this can greatly reduce the size of the inverse problem while retaining
the same quality of interpolation.

The gradient boosting algorithm allows us to fit the equivalent source model
iteratively by operating on individual overlapping windows.
As a result, our method solves several much smaller least-squares problems
instead of a large one.
This has some similarities with the strategy used by \citet{leao1989} but
without the requirement for sources and predictions to be on regular grids.

Through tests on synthetic data, we show that:
(i)~the \emph{block-averaged} sources are able to achieve the same accuracy as
other traditional equivalent source layouts while using a fraction of the
number of sources, and
(ii)~the \emph{gradient boosting} algorithm greatly reduces the computational
memory required to fit very large datasets without sacrificing prediction
accuracy.
Finally, a combination of both strategies is used to process a collection of
approximately 1.7 million ground gravity data measurements from Australia.
